The effect of genetic linkage on island endemics richness

### 2018-08-20 paper/draft.tex
results: temporal dynamics of radiations FL vs NL

>>>>

\subsection{Single species scenarios}
Species evolving on its own without interference from other species showed complex and dynamic speciation/differentiation patterns.
While low-linkage lineages adapted to the new environmental conditions on the island within some thousand timesteps to produce distinct populations,
high-linkage lineages were noticeably slower to differentiate.
Several 10.000 years later, however, high-linkage lineages began with strong radiations, thus surpassing species numbers as compared to low-linkage scenarios.

\begin{figure}
  %\includegraphics{}
  \caption{[2 x 2]
    Emerging numbers of species (and average population sizes) over time.
    Low-linkage lineages in COLOR1, high-linkage lineages in COLOR2.
    Top row: lineages simulated in isolation.
    Bottom row: simulated communities.}
  \label{specieslinkage}
\end{figure}
